Bayesian Neural Networks

### 2024-04-03 Paper/paper.tex

\subsection{History}

\begin{figure}[H]
	\begin{tikzpicture}[scale=0.5,every node/.style={outer sep=5pt}]
		%Notation: {year, the title of the event}
		%NOTE! Everyting is zero-based
		\def\ourInfo{{
				{"1987"," The patent a 'Method of providing digital signatures' is filed by Ralph C. Merkle\cite{merkle-patent}."},
				{"1999","The original patent expires."},
				{"2009","Bitcoin uses Merkle Trees for 'block header commitment.'\cite{friedenbach_alm_2017}"},			
				{"2009","BitTorent uses Merkle Trees for data integrity\cite{bep30}."},
		}}
		\pgfmathsetmacro{\length}{3}% Zero based.

		% Loop through the array containing all events.
		\foreach \i in {0, ..., \length}{
			\pgfmathsetmacro{\year}{\ourInfo[\i][0]}% Get the left cell (year)
			\pgfmathsetmacro{\eventName}{\ourInfo[\i][1]}% Get the right cell (event name)
			\draw[thick,red] (0,-2*\i-2)--(0,-2*\i);% Draw vertical line
			\ifnum \i=0 % Should be in red text
			\draw(0,-2*\i-1) node[black, right, align = left]{\eventName};% Display the event name
			\draw(0,-2*\i-1) node[black, left] {\year};
			\else % Should be in black text
			\draw(0,-2*\i-1) node[right, black]{\eventName};% Display the event name
			\draw(0,-2*\i-1) node[left] {\year};% Display the year
			\fi
		}
		% Draw the bullet with the dash
		\foreach \i in {0, ..., \length}{
			\filldraw[draw = white, fill = red,thick] (0,-2*\i-1) circle (5pt);
			\draw[thick,red] (-12pt,-2*\i-1)--(0,-2*\i-1);
		}
	\end{tikzpicture}
\end{figure}

\section{Neural Network}

>>>>

\section{Machine Learning}

% To understand the concept of deep learning, we first need to understand the broader area it is considered a subset of; machine learning. 
%Machine learning is considered to be a branch of artificial intelligence (AI) with the goal to help AI “learn” more, but specifically in a way that imitates the human process of learning through the use of data and algorithms\cite{ibmWhatIsML}. 
Machine learning includes a variety of topics of which artifical intelligence (AI) and neural networks are a subset. Neural networks in particular involve an abstract imitation of the human brain using simulated neurons which is trained on data using particular algorithms.

The term supervised learning refers to a specific common method of machine learning which uses a labeled dataset to train a model to correctly predict the labels via some training algorithm. A classification problem in supervised learning involves predictions where all labels are grouped into a set of categories. The training process can be broken down into three major steps, which include a decision process, an error function, and an optimization process \cite{berkelyWhatIsML}. The decision process is the set of steps the algorithm takes after receiving the data based on the goal of the model. The second step in the process is the error function, which is the method of measuring chosen to see if the algorithm gave a “good” or “bad” input. The two most common choices of the error function is a simple yes or no on if a data point was classified correctly in the case of classification, or the difference in value between the predicted outcome and the actual observed outcome for continuous values. Finally, the third and last step is the part of the process that implements learning. This step, the updating or optimization process, requires the algorithm to review the past data and outputs of the error function in order to better correct its decision making process in the future.

Throughout this report, we’ll often use the terms machine learning, deep learning, and neural networks. It is important to note that although these are fundamentally related fields, deep learning is a subfield of neural networks that in particular focuses on more complicated neural networks, while neural networks are a subfield in machine learning.

We will be training a classifier on labeled images in a supervised learning process to predict what is depicted in the image from a range of possibilities such as dog, cat, and plane.

% EDIT THIS SECTION But, back to deep learning! What sets deep learning apart from the more general machine learning is that unlike the supervised learning process that was described before, deep learning does not necessarily have to use pre labelled data sets. It can, if required, but the point of a deep learning algorithm is that one feature of the algorithm is that it itself can distinguish between the different types of data purely by looking at the data. This process of built in categorical distinction is extremely helpful, as it limits human interaction and interventions that are required in the learning process, as large amounts of data do not need to be “processed by hand” in order for the algorithm to make use of them (2). Deep learning models work through a “layering” process, where multiple layers of the original three steps listed above work together in the algorithmic process.

\subsection{Neural Network}
